---
title: "Workshop 2: Distribution and its Tendency"
author: "Bolun"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "AnnArbor"
    colortheme: "dolphin"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Review

* Hope everyone successfully installed R and Rstudio, otherwise, please still use Rstudio Cloud today and contact me after the workshop to figure it out.

* Frequency Distribution: A frequency distribution is an overview of all distinct values in some variable and the number of times they occur.

* Relative Frequency Distribution: A relative frequency distribution shows the proportion of the total number of observations associated with each value or class of values

* Example, transform a histogram to relative frequency distribution, how you could do that?.

## Warming up 

Before we move into today's topic, let's warm up by loading some data sets into R

* go to https://gss.norc.org/get-the-data/stata and download data from 2008 and 2016

* set your working directory.

* using the following code to load the data.

```{r echo = T, eval = FALSE}
install.packages("haven")
library(haven)
gss2008 <- read_dta("[replace your path here]/GSS2008.dta")
gss2016 <- read_dta("[replace your path here]/GSS2016.dta")
```

## Shape of the Distribution 1

Group Activity: More visualization, but use ggplot2. You can refer to https://ggplot2.tidyverse.org/reference/geom_histogram.html and the example code.

* Using the GSS data to plot histograms for income, age and number of children.
* Turn the histogram into relative frequency distribution (or density distribution)
* What can you read out of the plots? To which direction the skewness is towards?

## Shape of the Distribution 2

Briefing your findings:

* To which direction the skewness is towards?
* Is there any difference across years? What does the difference imply?

## Tendency and the shape, part 1

Group Activity: Adding vertical lines of mean, median and mode to your previous visualization. 

You can use the following code to get the mean, median and mode. 
```{r echo = TRUE, eval = FALSE}
data <- c(1:10, 5, NA)
data_median <- median(data, na.rm = TRUE)
data_mean <- mean(data, na.rm = TRUE)
data_mode <- mode(data, na.rm = TRUE)
```

You can add a vertical line by using
```{r echo = TRUE, eval = FALSE}
ggplot(data, aes(x = x)) + 
  geom_histogram() + 
  geom_vline(xintercept = value)
```

## Tendency and the shape, part 2

Group Discussion: 

Based on the visualization, each group discuss a variable from the three.

* What do you notice? 
* How do the three different lines locate in the graph? Why is it the case?
* Optional: can you tell the positions of mean, median and mode and their relation with the skewness?

## Probability Distribution 1

Probability distribution: you can see probability distribution as a special kind of relative frequency distribution. Instead of being created out of a sample/dataset, it is generated via a formula. 

* Using binomial probability distribution as an example.  
* Imagine that you are really good at flipping coin, so in a Sunday afternoon you flip the coin for 40 times. How many heads would you find in these 40 trials? 
* Simulating the situation: you are stuck at home because of COVID, you decide to do the same trial for 500 times. 
* More math please refer to https://en.wikipedia.org/wiki/Binomial_distribution

## Probability Distribution 2

Group Activity: Adjust the p in the simulation, what do you find the difference in the probabilty distribution?

## Closer

Next time, we will discuss inference, that is, how much we can tell about a population from a sample?

* Review what is sample and what is population. 



