---
title: "Review Section"
author: "Bolun Zhang, UCSD Sociology"
date: "2/1/2021"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Outline

Here we will go through the main points in descriptive statistics, sampling 
distribution and also point estimator. 

* Mean, standard deviation, median, mode, and range of your sample dataset.

* Identify the lower quartile, upper quartile, and interquartile range of your 
sample dataset.

* Sampling Distribution and Point Estimates
  + What is the estimated standard error of the sample mean?
  + Using the t distribution table (from the textbook appendix or the lecture 
notes), identify a 95% confidence interval for the population mean.

## So, Let's imagine a scenario

We are back in the 1000-population island

```{r , echo = TRUE}
set.seed(92037)
pop_height <- rnorm(1000, mean = 1.7, sd = 0.15)
pop_height <- round(pop_height, 2)
sample_height <- sample(pop_height, 20)
sample_height
```

## Mean

We can calculate the mean by

$$Mean = \sum{height}/20$$
$$= (1.70 + 2.06 + 2.01 + 1.49...... + 1.61+1.43 +1.71 )/20$$

## Mean

The final result is 
```{r, echo = FALSE}
sample_mean <- mean(sample_height)
print(sample_mean)
```

## Median

We first arrange the 20 people according to their heights

```{r, echo = FALSE}
sort(sample_height)
```

The median is $$(1.64+1.69)/2 = 1.665$$
```{r, echo = TRUE}
median(sample_height)
```

## Mode

So, what is the mode in this sample? 

## The Range of the the sample

```{r}
print(paste("the minimum is", min(sample_height)))
print(paste("the maximum is", max(sample_height)))
```

## Standard Deviation

$$s = \sqrt{\frac{\sum(x_i-\bar{x})^2}{n}}$$
In our case, it equals

$$ s = \sqrt{\frac{(1.36-1.6815)^2 + (1.43-1.6815)^2...(2.06-1.6815)^2}{20}} $$

## Standard Deviation

The result is 

```{r}
div <- sample_height - sample_mean
div2 <- div^2
s <- (sum(div2)/20)^(0.5)
print(paste("The standard deivation of the sample is",s))
```

If you tried:
```{r, echo = TRUE}
sd(sample_height)
```

Why are they different?

## Quartile

The lower quartile is $$(1.57+1.60)/2 = 1.585$$ and the upper quartile is $$(1.74+1.79)/2=1.765$$

## You might wonder...if you tried

Just want you know, quartile is actually a more complicated issue. If you compare the result from the textbook method and result from the code:

```{r, echo = TRUE}
quantile(sample_height)
```

For more, please refer to https://en.m.wikipedia.org/wiki/Quartile. R is using method 4 to calculate the quartile. 

## Estimated Standard Error

As a reminder, the old-fashioned formula to estimate standard error is

$$\sigma_{\bar{x}} \approx \frac{s}{\sqrt{n}}$$

Thus, we can calculate the standard error $\sigma = 0.183/\sqrt{20}$

```{r}
sigma <- s/(20)^(1/2)
print(sigma)
```

## Student Distribution

We simulate this in the last workshop. 

$$t = \frac{\bar{X}-\mu_0}{s/\sqrt{n}}$$

Thus you can understand why the confidence intervals are $\pm{T_{0.025}*SE}$. 

Here the degree of freedom is $20-1 = 19$, we can find the t-score in the table.

```{r}
t <- dt(0.025, df = 19)
dt(0.025, df = 19)
```

Thus the confidence intervals of the sample mean is $\pm{(0.394*0.183)}$




